A holomorphic approach to membranes and fivebranes

### 2022-07-20 fivebranes/kr.tex
merge

\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
\usepackage{macros-fivebrane}
%
\begin{document}

@@

The (super) character of an $E(3|6)$-module $M$ is given by the formula
\[
\ch (M) \define {\rm tr}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
\]
Our goal in this section is to compute the explicit formula for this character in the case of the degenerate modules $I_A(\lambda_1,\lambda_3)$ of type $A$ (and its modified version $\til I_A(\lambda_1,\lambda_3)$) which are irreducible quotients of the Verma modules $M_A(\lambda_1,\lambda_3)$ (respectively, $\til M_A(\lambda_1,\lambda_3)$).

As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
\[
M(V) = \Sym(\lie{g}_{<0}) \otimes V .
\]
%We define the modified character of a Verma module by the formula
%\[
%\til{\ch} \, M(V) = \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) \cdot \ch (V) \left(q^{-1}, t_1^{-1}, t_2^{-1}, r^{-1} \right)  .
%\]
Define
\[
R(q,t_1,t_2,r) \define \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) ,
\]
so that the character of the Verma module $M(V)$ is a product of $R$ with the character of the finite-dimensional $\fg_0$-representation $V$.
In the computations of the sections that follow we will make the substitution $\boxed{q = t^2}$ for notational simplicity.

@@

The first ingredient in determining an explicit formula for the modified character of type $A$ Verma modules is a direct calculation.
\begin{lem}
\label{lem:R}
The explicit formula for $R = R(t,t_1,t_2,r)$ is
%\beqn
%R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
%\eeqn
\beqn
R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
\eeqn
\end{lem}

Recall that the type $A$ degenerate modules are defined by induction from the $\fg_0$-module 
\[
V = V^{\lambda_1,\lambda_3}_A \subset \C[z_i,w_a]
\] 
given by polynomials of homogenous degree $\lambda_1,\lambda_3$ in the variables $z_i,w_a$ respectively.
Thus, we have the following explicit presentation for the modified character of type $A$ modules. 
\begin{prop}
One has
\beqn\label{eqn:MA}
\ch \, \til M_A(\lambda_1,\lambda_3) = q^{y} R(q,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r)
\eeqn
where $y = \lambda_1 - \frac32 \lambda_3$, $R$ is as in Lemma \ref{lem:R} and 
\beqn\label{eqn:su}
\ch(V_A^{\lambda_1,\lambda_3})(t_1,t_2,r) = \ch_{SU(3)}^{\lambda_1}(t_1,t_2) \ch_{SU(2)}^{\lambda_3} (r) 
\eeqn
is the $SU(3) \times SU(2)$ character of the representation $V_A^{\lambda_1,\lambda_3}$. 
\end{prop}

@@

We proceed to evaluate the sum in \eqref{eqn:chA1}
\begin{multline}
t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1} \sum_{j \geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) R \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \left(\frac{1 - (t_1^2 t_2^{-1})^{\lambda_1 + j + 1}}{1 - t_1^2 t_2^{-1}} - t_1^{-1} t_2^{-1} \frac{1 - (t_1 t_2^{-2})^{\lambda_1 + j + 1}}{1 - t_1 t_2^{-2}} \right) \\ =
\frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \times \\ 
\left[(1-t_1 t_2^{-2})(1-(t_1^2 t_2^{-1})^{\lambda_1+j+1}) - t_1^{-1}t_2^{-1} (1-t_1^2 t_2^{-1}) (1 - (t_1 t_2^{-2})^{\lambda_1+j+1}) \right]
%
%\\ = \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \\ \times \left(1 + t_1^{2\lambda_1 +2j+3}t_2^{-\lambda_1-j-1} - t_1 t_2^{-2} - t_1^{2 \lambda_1 + 2j + 2} t_2^{-\lambda_1 - j -1} \right. \\ \left. - t_1^{-1} t_2^{-1} + t_1^{\lambda_1+j+2} t_2^{-2 \lambda_1 - 2j-4} + t_1 t_2^{-2} + t_1^{\lambda_1 + j} t_2^{-2\lambda_1 - 2 j - 3} \right)
\end{multline}

We split the sum $\sum_{j \geq 0}$ into four terms
\begin{itemize}
\item the first term is 
\beqn
(1-t_1t_2^{-2}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{2 \lambda_1 + j + 2} t_2^{-\lambda_1 - 1} \right) .
\eeqn
Evaluating the infinite series this becomes
\begin{multline} 
r^{\lambda_3} (1-t_1 t_2^{-2}) \left(\frac1{1-trt_1^{-1}t_2} - \frac{t_1^{2\lambda_1+2}t_2^{-\lambda_1-1}}{1 - t r t_1} \right) \\ = \frac{r^{\lambda_3}(1-t_1 t_2^{-2})}{(1-trt_1^{-1}t_2)(1 - t r t_1)} \left(1 - trt_1-t_1^{2\lambda_1+2} t_2^{-\lambda_1-1}+tr t_1^{2 \lambda_1+1} t_2^{-\lambda_2}\right)
\end{multline}
\item the second term is
\beqn
t_1^{-1} t_2^{-1}(1-t_1^2 t_2^{-1}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{\lambda_1+1} t_2^{-2\lambda_1 - j - 2}\right) .
\eeqn
\end{itemize}

Combining with the formula for $R(t,r,t_1,t_2)$ we arrive at the formula
\begin{multline} 
\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} 
\end{multline}

\parsec
In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$.

@@

\begin{proof}
In this specialization it is easy to see that 
\[
\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} ,
\]
which is just the dimension of polynomials of homogenous degree $\lambda_1+j$ in three variables.

We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:chA2}:
\beqn
\ch \til M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{2 \lambda_1-3\lambda_3} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^{-j} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
\eeqn
where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$
\[
R(t,r) = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} ,
\]
which we read off from Lemma \ref{lem:R}.
In this expression we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$: 
\[
r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
\]

@@

Finally, for general $\lambda_1,\lambda_3$ we specialize further $t=r$ and substitute $q = t^2$ to obtain
\beqn
\ch \til I_A(\lambda_1,\lambda_3) = \frac{q^{\lambda_1-\lambda_3+1}}{1-q} .
\eeqn

\subsection{Characters for degenerate modules of type B} \label{s:typeB}

>>>>

%\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}
%
%\begin{document}

@@

The (super) character of an $E(3|6)$-module $M$ is given by the formula
\[
\ch (M) \define {\rm str}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
\]
Our goal in this section is to compute the explicit formula for this character in the case of the degenerate modules $I_A(\lambda_1,\lambda_3)$ of type $A$ (and its modified version $\til I_A(\lambda_1,\lambda_3)$) which are irreducible quotients of the Verma modules $M_A(\lambda_1,\lambda_3)$ (respectively, $\til M_A(\lambda_1,\lambda_3)$).

@@

As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
\[
M(V) = \Sym(\lie{g}_{<0}) \otimes V .
\]
%We define the modified character of a Verma module by the formula
%\[
%\til{\ch} \, M(V) = \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) \cdot \ch (V) \left(q^{-1}, t_1^{-1}, t_2^{-1}, r^{-1} \right)  .
%\]
Define
\[
R(q,t_1,t_2,r) \define \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) ,
\]
so that the character of the Verma module $M(V)$ is a product of $R$ with the character of the finite-dimensional $\fg_0$-representation $V$
\[
\ch M(V) (q,t_1,t_2,r) = R(q,t_1,t_2,r) \cdot \ch (V) (q,t_1,t_2,r).
\]
In the computations of the sections that follow we will make the substitution $\boxed{q = t^2}$ for notational simplicity.

The first ingredient in determining an explicit formula for Verma modules is a direct calculation.
\begin{lem}
\label{lem:R}
The explicit formula for $R = R(t,t_1,t_2,r)$ is
%\beqn
%R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
%\eeqn
\beqn
R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
\eeqn
\end{lem}

Recall that the type $A$ degenerate modules are defined by induction from the $\fg_0$-module 
\[
V = V^{\lambda_1,\lambda_3}_A \subset \C[z_i,w_a]
\] 
given by polynomials of homogenous degree $\lambda_1,\lambda_3$ in the variables $z_i,w_a$ respectively.
Thus, we have the following explicit presentation for the modified character of type $A$ modules. 
\begin{prop}
One has
\beqn\label{eqn:MA}
\ch \, \til M_A(\lambda_1,\lambda_3) = q^{y} R(t,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r)
\eeqn
where $y = \lambda_1 - \frac32 \lambda_3$, $R$ is as in Lemma \ref{lem:R} and 
\beqn\label{eqn:su}
\ch(V_A^{\lambda_1,\lambda_3})(t_1,t_2,r) = \ch_{SU(3)}^{\lambda_1}(t_1,t_2) \ch_{SU(2)}^{\lambda_3} (r) 
\eeqn
is the $SU(3) \times SU(2)$ character of the representation $V_A^{\lambda_1,\lambda_3}$. 
\end{prop}

@@

\parsec[s:unrefinedA]

In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$.

@@

\begin{proof}
In this specialization we just see the dimension of the highest weight $SU(3)$ representations
\[
\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} .
\]

We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:chA2}:
\beqn\label{eqn:MA2}
\ch \til M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{2 \lambda_1-3\lambda_3-j} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
\eeqn
where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$ from Lemma \ref{lem:R}:
\[
R(t,r) = R|_{t_1=t_2=1} = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} .
\]
In equation \eqref{eqn:MA2} we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$. 
%\[
%r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
%\]

@@

Finally, for general $\lambda_1,\lambda_3$ we specialize further $t=r$ and substitute $q = t^2$ to obtain
\beqn
\ch \til I_A(\lambda_1,\lambda_3) = \frac{t^{2 \lambda_1 - 2 \lambda_3 + 2}}{1 - t^2} = \frac{q^{\lambda_1-\lambda_3+1}}{1-q} .
\eeqn

\parsec[s:refinedA]

We now turn to the formula for the totally unrefined character of $\til I_A(\lambda_1,\lambda_3)$, before specializing $t_1=t_2=1$.
The character will be given in terms of a generating function for highest weight $SU(3)$ representations.

Our first aim is to deduce a closed formula for the following generating function
\beqn
\til p^{\lambda_1} (x,t_1,t_2) = \sum_{j \geq 0} \ch_{SU(3)}^{\lambda_3+j} (t_1^{-1},t_2^{-1}) x^j .
\eeqn
where we recall that $\ch_{SU(3)}^{\lambda_3+j} (t_1,t_2)$ is the $SU(3)$ character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1+j,0)$. 
It will be convenient to define the polynomial 
\beqn\label{eqn:h1}
h_{\lambda_1}(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_2 -2}\right)  .
\eeqn

\begin{lem}
One has
\beqn
\til p_{\lambda_1} (x,t_1,t_2) = \frac{p_{\lambda_1}(x,t_1,t_2)}{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)} .
\eeqn
where the polynomial $p_{\lambda_1}(x,t_1,t_2)$ is given by
\beqn
p_{\lambda_1}(x,t_1,t_2) = 1 + (1+t_1 t_2 - t_2 x) h(t_1,t_2,x)
\eeqn 
\end{lem} 
\begin{proof}
\begin{multline}
t_1^{\lambda_1} t_2^{-\lambda_1} \sum_{j \geq 0} t_1^{j} t_2^{-j} x^j \sum_{k=0}^{\lambda_1 + j}t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \sum_{k=0}^{\lambda_1 + j} t_1^{j-k} t_2^{-j+2k} x^j \left(1 - t_1^{-k-1} t_2^{-k-1}\right) \\ 
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \left(t_1^j t_2^{-j} \frac{1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}}{1-t_1^{-1} t_2^{2}} - t_1^{j-1} t_2^{-j-1} \frac{1 - (t_1^{-2} t_2)^{\lambda_1+j+1}}{1 - t_1^{-2} t_2} \right) x^j  \\
%= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{2})} \sum_{j \geq 0} \left( t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1})(1 - t_1^{-2} t_2) \right. \\ \left. - t_1^{j-1} t_2^{-j-1} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1})(1-t_1^{-1} t_2^{2}) \right) x^j \\ 
= F(t_1,t_2) \left( G_1 (t_1,t_2,x) - t_1^{-1} t_2^{-1} G_2 (t_1,t_2,x)\right) .
\end{multline}

Where
\begin{itemize}
\item $F(t_1,t_2) = \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{-1}) (1-t_1^{-1} t_2^{2}) (1 - t_1^{-2} t_2)}$. 
\item $G_1(t_1,t_2,x) = \frac{1}{1 - t_1^{-1} t_2^2} \sum_{j \geq 0}  t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}) x^j$. 
\item $G_2(t_1,t_2,x) = \frac{1}{1 - t_1^{-2} t_2}\sum_{j \geq 0} t_1^{j} t_2^{-j} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1}) x^j$. 
\end{itemize}
%
%Directly, we compute
%\begin{align*}
%G_1(t_1,t_2,x) & = \frac{1}{1 - t_1 t_2^{-1} x} - \frac{t_1^{-\lambda_1-1} t_2^{2 \lambda_1 + 2}}{1 - t_2 x} \\
%G_2(t_1,t_2,x) & = \frac{1}{1-t_1 t_2^{-1} x} - \frac{t_1^{-2\lambda_1-2}t_2^{\lambda_1+1}}{1-t_1^{-1}x}
%\end{align*}
We state an intermediate lemma.
\begin{lem}
One has
\begin{align*}
G_1(t_1,t_2,x) & = \frac{1}{(1 - t_1 t_2^{-1} x)(1-t_2 x)} \big(1 + h(t_1,t_2,x) \big) \\
G_2(t_1,t_2,x) & = \frac{1}{(1 - t_1 t_2^{-1} x)(1-t_1^{-1} x)} \left(1 + t_1^{-1} t_2^{-1} h(t_1,t_2,x) \right) .
\end{align*}
where $h_{\lambda_1}(t_1,t_2,x)$ is as in equation \eqref{eqn:h}. 
\end{lem}

\begin{proof}
Formally evaluating the sum over $j$ we obtain
\begin{align*}
G_1(t_1,t_2,x) & = \frac{1}{1 - t_1^{-1} t_2^2} \left(\frac{1}{1 - t_1 t_2^{-1} x} - \frac{t_1^{-\lambda_1-1} t_2^{2 \lambda_1 + 2}}{1 - t_2 x} \right) \\
G_2(t_1,t_2,x) & = \frac{1}{1 - t_1^{-2} t_2} \left(\frac{1}{1-t_1 t_2^{-1} x} - \frac{t_1^{-2\lambda_1-2}t_2^{\lambda_1+1}}{1-t_1^{-1}x}\right) .
\end{align*}

Write $G_1 = g_1 / (1- t_1^{-1} t_2^2)$ and consider the polynomial
\beqn
\label{eqn:h2}
 (1-t_2 x)(1-t_1 t_2^{-1} x) g_1(t_1,t_2,x)
= 1 - t_1^{-\lambda_1} t_2^{2 \lambda_1 + 1} - t_2 x + t_1^{-\lambda_1} t_2^{2 \lambda_1 + 1} x .
\eeqn
This polynomial is clearly divisible by $1-t_1^{-1} t_2^2$ so we can define the polynomial
\beqn
\til h_{\lambda_1}(t_1,t_2,x) = \frac{(1-t_2 x)(1-t_1 t_2^{-1} x) g_1(t_1,t_2,x)}{1-t_1^{-1} t_2^2} 
\eeqn
By definition we have
\beqn
G_1(t_1,t_2,x) = \frac{\til h (t_1, t_2,x)}{(1-t_2 x)(1-t_1 t_2^{-1} x)} .
\eeqn

We are interested in the polynomial $h_{\lambda_1} = \til h_{\lambda_1} - 1$. 
By equation \eqref{eqn:h2} we see that 
\beqn
h_{\lambda_1} (t_1,t_2,x) = \frac{t_2 (t_1^{-1} t_2 - x) (1-t_1^{-\lambda_1} t_2^{2\lambda_1})}{1-t_1^{-1} t_2^2} .
\eeqn
The lemma immediately follows.
%\beqn
%h(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_2 -2}\right)  .
%\eeqn
\end{proof}

From this lemma we conclude that
\beqn
\til{p}_{\lambda_1}(t_1,t_2,x) = \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)}} \left(1 + (1+t_1 t_2 - t_2 x) h(t_1,t_2,x)\right)
\eeqn
and the result follows.
\end{proof}

%\begin{multline}
%t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1} \sum_{j \geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) R \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
%= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
%= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \left(\frac{1 - (t_1^2 t_2^{-1})^{\lambda_1 + j + 1}}{1 - t_1^2 t_2^{-1}} - t_1^{-1} t_2^{-1} \frac{1 - (t_1 t_2^{-2})^{\lambda_1 + j + 1}}{1 - t_1 t_2^{-2}} \right) \\ =
%\frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \times \\ 
%\left[(1-t_1 t_2^{-2})(1-(t_1^2 t_2^{-1})^{\lambda_1+j+1}) - t_1^{-1}t_2^{-1} (1-t_1^2 t_2^{-1}) (1 - (t_1 t_2^{-2})^{\lambda_1+j+1}) \right]
%%
%%\\ = \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \\ \times \left(1 + t_1^{2\lambda_1 +2j+3}t_2^{-\lambda_1-j-1} - t_1 t_2^{-2} - t_1^{2 \lambda_1 + 2j + 2} t_2^{-\lambda_1 - j -1} \right. \\ \left. - t_1^{-1} t_2^{-1} + t_1^{\lambda_1+j+2} t_2^{-2 \lambda_1 - 2j-4} + t_1 t_2^{-2} + t_1^{\lambda_1 + j} t_2^{-2\lambda_1 - 2 j - 3} \right)
%\end{multline}
%
%We split the sum $\sum_{j \geq 0}$ into four terms
%\begin{itemize}
%\item the first term is 
%\beqn
%(1-t_1t_2^{-2}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{2 \lambda_1 + j + 2} t_2^{-\lambda_1 - 1} \right) .
%\eeqn
%Evaluating the infinite series this becomes
%\begin{multline} 
%r^{\lambda_3} (1-t_1 t_2^{-2}) \left(\frac1{1-trt_1^{-1}t_2} - \frac{t_1^{2\lambda_1+2}t_2^{-\lambda_1-1}}{1 - t r t_1} \right) \\ = \frac{r^{\lambda_3}(1-t_1 t_2^{-2})}{(1-trt_1^{-1}t_2)(1 - t r t_1)} \left(1 - trt_1-t_1^{2\lambda_1+2} t_2^{-\lambda_1-1}+tr t_1^{2 \lambda_1+1} t_2^{-\lambda_2}\right)
%\end{multline}
%\item the second term is
%\beqn
%t_1^{-1} t_2^{-1}(1-t_1^2 t_2^{-1}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{\lambda_1+1} t_2^{-2\lambda_1 - j - 2}\right) .
%\eeqn
%\end{itemize}
\subsection{Characters for degenerate modules of type B} \label{s:typeB}
